% resume.tex
% vim:set ft=tex spell:

\documentclass[10pt,letterpaper]{article}
\usepackage[letterpaper,margin=0.75in]{geometry}
\usepackage[utf8]{inputenc}
\usepackage{mdwlist}
\usepackage[T1]{fontenc}
\usepackage{textcomp}
\usepackage{tgpagella}
\pagestyle{empty}
\setlength{\tabcolsep}{0em}

% indentsection style, used for sections that aren't already in lists
% that need indentation to the level of all text in the document
\newenvironment{indentsection}[1]%
{\begin{list}{}%
	{\setlength{\leftmargin}{#1}}%
	\item[]%
}
{\end{list}}

% opposite of above; bump a section back toward the left margin
\newenvironment{unindentsection}[1]%
{\begin{list}{}%
	{\setlength{\leftmargin}{-0.5#1}}%
	\item[]%
}
{\end{list}}

% format two pieces of text, one left aligned and one right aligned
\newcommand{\headerrow}[2]
{\begin{tabular*}{\linewidth}{l@{\extracolsep{\fill}}r}
	#1 &
	#2 \\
\end{tabular*}}

% make "C++" look pretty when used in text by touching up the plus signs
\newcommand{\CPP}
{C\nolinebreak[4]\hspace{-.05em}\raisebox{.22ex}{\footnotesize\bf ++}}

% and the actual content starts here
\begin{document}

\begin{center}
{\LARGE \textbf{Miguel Angel Aníbal Davor Fuenzalida Pino}}

\ \ Santiago, Chile\ \ \textbullet\ \ (+56) 9 85576767\ \ \textbullet
\ \ anibaldavor@gmail.com\ \ \textbullet\ \ github.com/nigue
\end{center}

\hrule
\vspace{-0.4em}
\subsection*{Experience}

\begin{itemize}
	\parskip=0.1em

	\item
	\headerrow
		{\textbf{Orange People}}
		{\textbf{Santiago}}
	\\
	\headerrow
		{\emph{Java Software Developer \& Project Manager}}
		{\emph{2010 -- 2012}}
	\begin{itemize*}
		\item Development on chilean online payment engine webpay.
		\item Making web services "webpay" related.
		\item Java interface programming via JSF technologies like PrimeFaces.
		\item Using hibernate on spring for managing data in a transactional way.
		\item Development of HTML, CSS, jquery sities.
	\end{itemize*}

	\item
	\headerrow
		{\textbf{Neoingen}}
		{\textbf{Santiago}}
	\\
	\headerrow
		{\emph{Java Software Developer \& Contributing Community Member}}
		{\emph{2013 -- Present}}
	\begin{itemize*}
		\item Java development on capturing and sending mail using POP3 and IMAP respectively.
		\item Using java programing to SOAP protocols, REST services, MQ services on angularjs sites and Mobile applications (Android, ios).
		\item Programming of complex Quartz services with Spring.
		\item Batch programming services, such as reading space separated or csv files with spring.
		\item Java development services using technologies together: ssh, ftp, sftp.
		\item Operation and maintenance of DB2 databases with hibernate.
	\end{itemize*}

\end{itemize}


\hrule
\vspace{-0.4em}
\subsection*{Education}

\begin{itemize}
	\parskip=0.1em

	\item 
	\headerrow
		{\textbf{Universidad Tecnológica Metropolitana}}
		{\textbf{Santiago, Chile}}
	\\
	\headerrow
		{\emph{Computer Engineer}}
		{\emph{2006 -- 2012}}
	\begin{itemize*}
		\item Extra studies to XHTML, css3, grid960, Jquery, templating. 
		\item Work to obtain a Computer Engineer degree on Web Services y Rest, Spring DATA, Mybatis, postgreSQL, JSF, Primefaces, on Multi Maven Project called SEPA (Sistema de Estudiantes, Profesores y Administradores).
		\item Professional practice N° 1: Banco Monex, .net application development.
		\item Professional practice N° 2: Free Port Mc. Morran, server maintenance, housing data transfer between servers tape.
	\end{itemize*}

\end{itemize}


\hrule
\vspace{-0.4em}
\subsection*{Core Technical Skills}

\begin{indentsection}{\parindent}
\hyphenpenalty=1000
\begin{description*}
	\item[Technologies:]
	Linux (working level), maven, jsp, jsf, Spring (MVC, batch, data, webServices), Hibernate (JPA, DAO, Spring, cache, Criteria, Transaccional), Primefaces (Mobile), CXF, Jersey, JAX-RS, libgdx, jmonkey, POP3 gmail, IMAP gmail, csv google, maven-android, windows.
	\item[Languages:]
	C, \CPP, Java, android, JavaScript, \LaTeX, Lua, SQL (Mysql, db2, oracle, postgreSQL), MongoDB, Jquery, css, xhtml, xml, json.
	\item[Open Source Contributions:]
	github.com/nigue, all my public Projects.
	\item[Interests:]
	Develop Android projects, using technologies such as libgdx, jMonkey, ren-py, thanks to the programming in Maven.
	\item[Current research:]
	Learning about clojure, Android, Japanese.
	\item[Other Languages:]
	English
\end{description*}
\end{indentsection}

\end{document}
